```{r}
library(AHMbook)
library(tidyverse)
library(jtools)
library(effects)
library(visreg)
library(metafor)
library(lme4)
#library(mixedup)
```

```{r}
#make and tidy fake data
 x <- data.fn(M = 100, J = 1, mean.lambda = 12, beta1 = 0, beta2 = -1, beta3 = -1,
   mean.detection = 1, alpha1 = 0, alpha2 = 0, alpha3 = 0, show.plot = T)
 xx <- data.frame(forest=x$forest, elev=x$elev, abun=x$N)
  dat <-  xx%>%mutate(elev = scales::rescale(xx$elev, to=c(0,100)), forest=scales::rescale(xx$forest, to=c(0,100)))
dat$taxon="A"

 x <- data.fn(M = 100, J = 1, mean.lambda = 12, beta1 = 0, beta2 = -1, beta3 = -2,
   mean.detection = 1, alpha1 = 0, alpha2 = 0, alpha3 = 0, show.plot = T)
 xx <- data.frame(forest=x$forest, elev=x$elev, abun=x$N)
 dat1 <-  xx%>%mutate(elev = scales::rescale(xx$elev, to=c(0,100)), forest=scales::rescale(xx$forest, to=c(0,100)))
  dat1$taxon="B"

dat <-  rbind(dat, dat1)

mod <- glm(abun~forest*elev*taxon, data=dat, family=poisson)

plot(effects::allEffects(mod))

x.mult=visreg(mod, "forest", "elev",  overlay=T, partial=F, cond=list(taxon="A"))
x.mult=visreg(mod, "forest", "elev",  overlay=T, partial=F, cond=list(taxon="B"))

x.add <- visreg(mod, "forest", "elev", scale="response", cond=list(taxon="A"))
x.add <- visreg(mod, "forest", "elev", scale="response", cond=list(taxon="B"))


x.add$fit%>%ggplot(aes(x=forest))+geom_ribbon(aes(ymin=visregLwr,ymax=visregUpr, fill=as.factor(round(elev))),alpha=0.2)+geom_line(aes(y=visregFit, col=as.factor(round(elev))), lwd=2)+scale_color_viridis_d("ELEV")+theme_bw()+ylab("Predicted abundance")+xlab("forest (%)")+scale_fill_viridis_d("ELEV")

x.mult$fit%>%ggplot(aes(x=forest))+geom_ribbon(aes(ymin=visregLwr,ymax=visregUpr, fill=as.factor(round(elev))),alpha=0.2)+geom_line(aes(y=visregFit, col=as.factor(round(elev))), lwd=2)+scale_color_viridis_d("ELEV")+theme_bw()+ylab("Predicted abundance")+xlab("forest (%)")+scale_fill_viridis_d("ELEV")

